О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-27 pps-linear-bound/pps-linear-lower-bound.tex
Proofreading by Usachev - p. 15

\begin{problem}
	For $M\in\mathfrak{M}(m,n)$, how many times can the distance 1 occur in $M$?
\end{problem}
The answer for $m=2$ is given by Theorem~\ref{thm:minimeter_1_planar}.
For greater $m$, we will be brave enough to put forward the following conjecture.
\begin{conjecture}
	Consider $M\in\mathfrak{M}(m,n)$, $M_1,M_2\in M$, $|M_1 M_2| =1$.
	Then either $n = m+1$ or $M$ is a ``blowup'' of a facher set and distance 1 occurs in $M$
	not more than $1+\frac{(m-1)^2 - (m-1)}{2}$ times.
\end{conjecture}
Such as estimate is based on the number of edges in an $(m-2)$-dimensional simplex.

We want to conclude the list of conjectures with the one which looks the easiest to deal with.

\begin{conjecture}
	\label{hyp:prime_planar}
	For every $n \geq 3$, $d \geq 1$ there exists an \textbf{prime}
	set $M\in\mathfrak{M}(2,n)$ which
	contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.
\end{conjecture}
This conjecture gives the same claim with Theorem~\ref{thm:prime_with_desired_distance}, but for $m=2$.
Obviously, Theorem~\ref{thm:prime_with_unique_desired_distance} can be generalized (for $m=2$) into a similar conjecture.

>>>>

\begin{problem}
	How many times can the distance 1 occur in a set $M\in\mathfrak{M}(m,n)$?
\end{problem}
The answer for $m=2$ is given by Theorem~\ref{thm:minimeter_1_planar}.
For greater $m$, we will be bold enough to suggest the following conjecture.
\begin{conjecture}
	Consider $M\in\mathfrak{M}(m,n)$, $M_1,M_2\in M$, $|M_1 M_2| =1$.
	Then either $n = m+1$ or $M$ is a ``blowup'' of a facher set and distance 1 occurs in $M$
	no more than $1+\frac{(m-1)^2 - (m-1)}{2}$ times.
\end{conjecture}
Such estimate is based on the number of edges in an $(m-2)$-dimensional simplex.

We want to conclude the list of conjectures with the one which appears the easiest to deal with.

\begin{conjecture}
	\label{hyp:prime_planar}
	For every $n \geq 3$, $d \geq 1$ there exists an \textbf{prime}
	set $M\in\mathfrak{M}(2,n)$ which
	contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.
\end{conjecture}
This conjecture gives the same claim as Theorem~\ref{thm:prime_with_desired_distance} does, but for $m=2$.
Obviously, Theorem~\ref{thm:prime_with_unique_desired_distance} can be generalized (for $m=2$) into a similar conjecture.
